%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

%\profilepic{alice.jpeg} % Profile picture

\cvname{Isaac Klugman} % Your name

\cvdate{30 April 2001} % Date of birth
\cvaddress{Southampton} % Short address/location, use \newline if more than 1 line is required
\cvnumberphone{07858248752} % Phone number
\cvsite{isaacklugman.com} % Personal website
\cvmail{isaacklugman@gmail.com} % Email address

%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	 EDUCATION
%----------------------------------------------------------------------------------------

%\setskilllist{Python, Java}
\newcommand{\myEducationTable}{
	\begin{tabular}{l}
		\educationitem{2019-2023}{MEng Computer Science}{University of Southampton}
		\educationitem{2017-2019}{A Level}{Bexhill College}
		\educationitem{2017}{GCSE}{Bexhill 6th Form}
	\end{tabular}
}

\newcommand{\schoolgrades}{
	\begin{tabularx}{\linewidth}{XXXX}
		\multicolumn{2}{l}{\bfseries A Level} & \multicolumn{2}{l}{\bfseries GCSE} \\
		Maths & \centering A* & Maths & 8 (A*) \\
		Comp Sci & \centering A & Eng. Lang. & 8 (A*) \\
		Physics & \centering B & Eng. Lit.  & 6 (B) \\
		& & Computing & \centering A* \\
	\end{tabularx}
}


%----------------------------------------------------------------------------------------
%	 PROJECTS
%----------------------------------------------------------------------------------------

\newcommand{\projectsection}{
	\begin{projects}
		\projectitem{JavaFX Dashboard Application}{University of Southampton}{Developed as part of a second-year Software Engineering Group Project. Collaborated in a team of four to build a dashboard for a client that enables loading and visualization of data statistics and analytics. JavaFX was used to build the application and SQL was used as the backend.}
		\projectitem{Multi-person 3D Pose Estimation System}{University of Southampton}{A fourth-year Group Design Project where I was part of a five-member team. Initiated 2D pose estimation using an omnidirectional camera, followed by the transformation of 2D keypoints to 3D using a neural network and mmWave radars. Ensured smooth project progression by adhering to Agile development methodologies and holding regular client meetings. This project was built using Python, pytorch and Open3D.}
		\projectitem{Interactive Music Hypertext System}{University of Southampton}{This third-year individual project involved research into the application of hypertext structures and Interactive Digital Narratives in music consumption. The project resulted in an interactive interface built in C\# with Unity for listening to music with branching structures.}
		\projectitem{Head Pose Tracking Analysis Tools}{Audioscenic}{Designed multiple GUI applications to perform offline analysis of head pose tracking system performance. Important features include a heat-map for visualizing tracking at varied room positions and head orientations, and a tool for frame-by-frame analysis. These tools were built using Python, OpenCV, QT and VTK.}
		\projectitem{Online Notes Garden}{}{I actively maintain a collection of notes on my personal website. The site is hosted via GitHub pages and the deployment involves parsining notes from markdown via a static site generator, providing an interconnected web of ideas and promoting a richer study experience.}
	\end{projects}
}



%----------------------------------------------------------------------------------------
%	 PUBLICATIONS
%----------------------------------------------------------------------------------------

\newcommand{\publications}{
	\begin{twenty} % Environment for a short list with no descriptions
		\twentyitem{2023}{Real-time 3D Multi-person Pose Estimation using an Omnidirectional Camera and mmWave Radars}{}{Publication Title: 2023 International Conference on Engineering and Emerging Technologies (ICEET)}
	\end{twenty}
}



%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\newcommand{\experience}{
	\begin{twenty} % Environment for a list with descriptions
		\twentyitem{2023}{Computer Vision Research and Development: User Position Tracking Systems}{Audioscenic}{Led research initiatives focused on head pose estimation techniques viable up to five meters. Designed and implemented data visualization and collection tools as well as researching cutting-edge deep learning methodologies for pose estimation. My contributions led to the integration of these tools into the company's internal testing platforms, streamlining further development efforts.}
		\twentyitem{2021}{Barista}{Showcase Cinema, Costa}{This role involved performing openings and closings, till management and money handling, making and serving coffee, customer service and food handling.}
		\twentyitem{2019}{Customer Assistant}{Primark}{This role invovled serving customers at the till, money handling and maintaining a clean store front.}
		\twentyitem{2018-2019}{Barista Volunteer}{The Pelham}{This was a volunteer role and involved making and serving coffee, money handling and customer service.}
	\end{twenty}
}




%----------------------------------------------------------------------------------------
%	 INTERESTS
%----------------------------------------------------------------------------------------

\newcommand{\interests}{
	I am an eager self-learner and will always take the oppurtunity to continue my studies at home. As an alumni, I continue to study new things using the University resources - I am currently very interested in studying deep learning technologies for computer vision.
	
	Outside of my studies I am very passionate about music, I grew up learning violin, but am now a self taught guitarist and pianist. In addition to developing my own skills, I hope to start sharing my experience through online material for others who are starting. As well as writing my own music, I spend a lot of time listening to others' - I find my inspiration from bands and artists such as Pink Floyd, Fleetwood Mac, Elliot Smith, Billy Joel and David Bowie.
}